Predicting sales of newly published books

### 2015-10-22 paper.tex
fixing&improving the text, tanking into account some comments (thanks)

\begin{minipage}{2.3in} \begin{verbatim}
reference
author
retail pricer
subject1
subject2
subject3
editorial
collection
bookbinding
print-run
total sales
department stores sales
sales through delegates
rest of sales
total sales first year
mall sales first year
delegates sales first year
rest of sales first year
total distributed
distributed through department stores
distributed through delegates
distributed - rest
total distributed first year
distributed through department stores first year
distributed through delegates first year
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
rest of distributed first year
reprints
number of reprints
total returns
returns - department stores
delegates returns
rest of returns
total returns firt year
returns -  department stores first year
delegates returns first year
rest of returns first year
gifts
units distributed as novelty
total points of sale
points of sale - department stores
delegates points of sale
rest of points of sale
total points of sale first year
department stores points of sale first year
delegates points of sale first year
rest of points of sale first year
weeks for sale
positive sales environment
medium sales environment
negative sales environment
\end{verbatim} \end{minipage}    \\

@@

In this prediction problem, several variables related to the own book affect 
the forecasts, such as author, price, subject or publisher. %This has
                                %to be grounded by the experiment and
                                %graphs.

However, there are other external variables that also affect the sales of 
a new book, such as those related to seasonality, trends or promotions, 
that classical prediction methods can not deal with.
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. %so what?

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=stages.eps,width=7cm}
\caption{\small{Three main stages in this research: data analysis, (2) forecasting 
methods testing, and (3) subjectively adjusting the obtained results.}}
\label{fig:stages}
\end{center}
\end{figure}

Thus, in this study we propose three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
for details): 
\begin{itemize}

@@

  \item  Finally, in some cases, it is necessary a third stage where experienced 
  managers adjust subjectively the results obtained using the forecasting methods. 
  They might manually adjust the forecasting results taking into account their 
  knowledge in industry experience and their perception about trends.

@@

@@

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
first year, reprints, units distributed as novelty, weeks for sale, total sales}.

@@

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
%*************************************** Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analysis }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

@@

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with X variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  LR      & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis.}}
\label{tabla:resultsSOM}
\end{table*}

@@

In this sense, the decision trees proved to be a suitable model because of the 
ease to explain how the prediction is obtained from the variables that describe 
the new book. 
This, compared to the black-box models such as the artificial neural network 
was decisive from the point of view of the needs of experts and the company.
Moreover, proposed method was validated by the company and incorporated in a 
business intelligence tool for publishing houses. %FERGU: no hay más info de esto? estaría guay describirlo

@@

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by PreTEL (PRM Consultores - Trevenque),
SIPESCA (Programa Operativo FEDER de Andalucía 2007-2013), TIN2011-28627-C04-02 
and TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), PRY142/14
(Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
IX Convocatoria de Proyectos de Investigaci{\'o}n), and PYR-2014-17
GENIL project (CEI-BIOTIC Granada). 
    % ¿Y el contrato con Trevenque?  - JJ
    %[pedro] añadido

>>>>

\begin{minipage}{2.45in} \begin{verbatim}
reference
author
retail pricer
subject1
subject2
subject3
editorial
collection
bookbinding
print-run
total sales
dept stores sales
sales through delegates
rest of sales
total sales 1st year
mall sales 1st year
delegates sales 1st year
rest of sales 1st year
total distributed
distributed through dept stores
distributed through delegates
distributed - rest
total distributed 1st year
distrib. through dept stores 1st year
distrib. through delegates 1st year
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
rest of distributed 1st year
reprints
number of reprints
total returns
returns - dept stores
delegates returns
rest of returns
total returns firt year
returns -  dept stores 1st year
delegates returns 1st year
rest of returns 1st year
gifts
units distributed as novelty
total points of sale
points of sale - dept stores
delegates points of sale
rest of points of sale
total points of sale 1st year
dept stores points of sale 1st year
delegates points of sale 1st year
rest of points of sale 1st year
weeks for sale
positive sales environment
medium sales environment
negative sales environment
\end{verbatim} \end{minipage}    \\

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends or 
promotions, that classical prediction methods can not deal with.
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. %so what?

@@

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=stages.eps,width=7cm}
\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
methods testing, and (3) subjectively adjusting the obtained results.}}
\label{fig:stages}
\end{center}
\end{figure}

Thus, in this study two main stages are proposed: 
\begin{itemize}

@@

@@

In some cases, depending on the company needs and after obtaining the forecasting 
results, it is necessary a third stage where experienced 
managers adjust subjectively the results obtained using the forecasting methods 
(see Figure \ref{fig:stages} for details). 
They might manually adjust the forecasting results taking into account their 
knowledge in industry experience and their perception about trends.

@@

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

@@

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
%*************************************** Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analysis }

\textbf{ TODO: add the SOM analysis }

\textbf{ TODO: add the SOM analysis }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

@@

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset \textbf{with X variables} per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  LR      & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis.}}
\label{tabla:resultsSOM}
\end{table*}

@@

In this sense, the decision trees proved to be a suitable model because of the 
ease to explain how the prediction is obtained from the variables that describe 
the new book. 
This, compared to the black-box models such as the artificial neural network, 
was decisive from the point of view of the needs of experts and Trevenque company.
Moreover, proposed method was validated by the company and incorporated in a 
business intelligence tool for publishing houses. %FERGU: no hay más info de esto? estaría guay describirlo

@@

%********************************************************************************
\section*{Acknowledgements}
This work has been supported in part by 
PreTEL (PRM Consultores - Trevenque),
TIN2014-56494-C4-3-P (Spanish Ministry of Economy and Competitivity),
SPIP2014-01437 (Direcci{\'o}n General de Tr{\'a}fico), 
PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la
IX Convocatoria de Proyectos de Investigaci{\'o}n), 
and PYR-2014-17 GENIL project (CEI-BIOTIC Granada).
